---
title: "SOC-INFO data processing"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

```{r}
source(here::here("R/soc_info_helpers.R"))
#d_path <- "data/01_raw_data/goal_actions_ver3/full_sample/sandbox-results"
d_path <- "data/01_raw_data/goal_actions_ver4/production-results"
```

## Load raw json data

Use purrr to map our read json function over all files in the raw data directory

```{r}
files <- dir(here(d_path))
df_list <- files %>% purrr::map(~ safe_json_to_df(data_path = d_path, .)) 
```

Look at output to see where errors occurred and then convert to data frame only keeping successful function calls.

```{r}
results <- df_list %>% transpose() 
ok <- results$error %>% map_lgl(is_null)
df <- results$result %>% keep(ok) %>%  map_df(bind_rows)
```

## Data checks

How many participants in each condition?

```{r}
df %>% 
  distinct(workerid, condition, social_condition) %>% 
  count(condition, social_condition) %>% 
  knitr::kable()
```

Convert all strings to lower case.

```{r}
df %<>% mutate_if(is.character, str_to_lower)
```

## Anonymize Turker ids. 

```{r}
df_anonymized <- df %>% 
  select(workerid) %>% 
  distinct() %>% 
  mutate(id = 1:nrow(.)) 

df_wide <- left_join(df, df_anonymized, by = "workerid") %>% 
  select(id, everything(), -workerid)
```

## Clean up and variable creation

Score the manipulation check.

```{r}
actions <- c("button", "handle", "both")

# some string manipulation to get clean order variable
manip_check <- df_wide %>% 
  select(id, condition, outcome, contains("check")) %>% 
  rowwise() %>% 
  mutate(manip_check_order_action = str_sub(manip_check_order, 
                                            start = 1, 
                                            end = str_locate(manip_check_order, outcome)[1] - 1)
  )

# score the manipulation check
manip_check %<>% 
  mutate(manip_check_correct = ifelse(music_check_response == manip_check_order_action,
                                      TRUE, FALSE)) %>% 
  group_by(id) %>% 
  mutate(manip_check_score = sum(manip_check_correct)) %>% 
  select(id, condition, manip_check_score) %>% 
  unique()
```

Tidy up the data frame.

```{r}
prior <- df_wide %>% 
  select(id, condition, prior_beliefs, prior_hypothesis) %>% 
  mutate(hypothesis_type = "prior") %>% 
  rename(slider_value = prior_beliefs,
         hypothesis = prior_hypothesis)

posterior <- df_wide %>% 
  select(id, condition, posterior_beliefs, posterior_hypothesis) %>% 
  mutate(hypothesis_type = "posterior") %>% 
  rename(slider_value = posterior_beliefs,
         hypothesis = posterior_hypothesis)

d_final <- bind_rows(prior, posterior) %>% 
  mutate(slider_value = as.integer(slider_value))
```

Normalize the sliders.

```{r}
d_final %<>% 
  group_by(id, hypothesis_type) %>% 
  mutate(slider_value_normalized = round(slider_value / sum(slider_value), 3)) %>% 
  ungroup()
```

Add participant info.

```{r}
d_final %<>% left_join(., 
                       select(df_wide, id, condition, outcome,
                              browser:action_trial_time) %>% 
                         unique(),
                       by = c("id", "condition"))
```

Add manipulation check info.

```{r}
d_final %<>% left_join(., manip_check, by = c("id", "condition"))
```

Now join everything together and create some factor variables in the order we want for plotting.

```{r}
d_final %<>%
  left_join(., select(df_wide, id, 
                      condition, 
                      social_condition, 
                      action_response) %>% unique(),
            by = c("id", "condition"))
```

Clean up the hypothesis variable.

```{r}
d_final %<>%
  rowwise() %>% 
  mutate(hypothesis = str_sub(hypothesis, 
                              start = 1, 
                              end = str_locate(hypothesis, outcome)[1] - 1))
```

## Write to disk

```{r}
write_csv(d_final, path = here("/data/02_tidy_data", 
                               "goal_actions_no_soc_tidy.csv"))
```
