---
title: "SOC-INFO data processing"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

```{r}
library(lubridate); library(magrittr); library(jsonlite); library(tidyverse); library(here) 
```

```{r}
#d_path <- "data/01_raw_data/goal_actions/pilotB/production-results"
d_path <- "data/01_raw_data/goal_actions_ver2/pilotA/sandbox-results/"
```

## Load raw json data

Write a function that reads the raw json, extacts the information we care about, and builds a tidy data frame

```{r}
# takes a list and extracts the information we care about
json_to_df <- function(data_path, file) {
  d <- read_json(path = here(data_path, file))
  d
}
  
  data.frame(
    workerid = d$WorkerId, 
    condition = d$answers$goal_condition,
     = d$answers$intial_response1 %>% unlist(),
    action_response = d$answers$action_response,
    prior_hypothesis = d$answers$hypotheses_slider_order_prior %>% unlist(),
    prior_beliefs = d$answers$prior_beliefs %>% unlist(),
    posterior_hypothesis = d$answers$hypotheses_slider_order_posterior %>% unlist(),
    posterior_beliefs = d$answers$posterior_beliefs %>% unlist(),
    browser = d$answers$browser,
    browser_width = d$answers$browser_width,
    browser_height = d$answers$browser_height,
    screen_width = d$answers$screen_width,
    screen_height = d$answers$screen_height,
    mobile_device = d$answers$mobile_device,
    about = d$answers$about,
    comment = d$answers$comment,
    age = d$answers$age,
    gender = d$answers$gender,
    first_language = d$answers$language,
    experiment_time = d$answers$experiment_completion_time / 1000,
    action_trial_time = d$answers$action_trial_time / 1000
  )
}
```

Use purrr to map our read json function over all files in the raw data directory

```{r}
files <- dir(here(d_path))
df <- files %>% purrr::map(~ json_to_df(data_path = d_path, .)) 
```

## Anonymize Turker ids. 

```{r}
df_anonymized <- df %>% 
  select(workerid) %>% 
  distinct() %>% 
  mutate(id = 1:nrow(.)) 

df_wide <- left_join(df, df_anonymized, by = "workerid") %>% 
  select(id, everything(), -workerid)
```

## Clean up and variable creation

Tidy up the data frame.

```{r}
prior <- df_wide %>% 
  select(id, condition, prior_beliefs, prior_hypothesis) %>% 
  mutate(hypothesis_type = "prior") %>% 
  rename(slider_value = prior_beliefs,
         hypothesis = prior_hypothesis)

posterior <- df_wide %>% 
  select(id, condition, posterior_beliefs, posterior_hypothesis) %>% 
  mutate(hypothesis_type = "posterior") %>% 
  rename(slider_value = posterior_beliefs,
         hypothesis = posterior_hypothesis)

d_final <- bind_rows(prior, posterior) %>% 
  mutate(slider_response_collapsed = ifelse(hypothesis == "Purple and Orange", 
                                            "both_buttons", 
                                            "single_button"),
         slider_value = as.integer(slider_value))
```

Normalize the sliders.

```{r}
d_final %<>% 
  group_by(id, hypothesis_type) %>% 
  mutate(slider_value_normalized = round(slider_value / sum(slider_value), 3)) %>% 
  ungroup()
```

Create variable that collapses across both single button responses.

```{r}
d_final_collapsed <- d_final %>% 
  group_by(id, hypothesis_type, slider_response_collapsed) %>% 
  mutate(slider_value_2 = sum(slider_value)) %>% 
  select(id, hypothesis_type, slider_response_collapsed, slider_value_2, condition) %>% 
  unique() %>% 
  group_by(id, hypothesis_type, condition) %>% 
  mutate(slider_value_norm_2 = round(slider_value_2 / sum(slider_value_2), 3)) %>% 
  select(id, hypothesis_type, condition, slider_response_collapsed, slider_value_norm_2)
```

Add the second normalized slider variable to the belief data frame.

```{r}
d_final %<>% left_join(., d_final_collapsed)
```

Add participant info.

```{r}
d_final %<>% left_join(., 
                         select(df_wide, id, condition, browser:action_trial_time) %>% unique(),
                         by = c("id", "condition"))
```

Now create a collaposed action response variable and add to the beliefs data frame

```{r}
df_wide %<>% mutate(action_response_collapsed = ifelse(action_response == "orange_and_purple", 
                                                       "both_buttons", 
                                                       "single_button"))
```

Now join everything together and create some factor variables in the order we want for plotting.

```{r}
d_final %<>%
  left_join(., select(df_wide, id, condition, action_response_collapsed, action_response) %>% unique(),
            by = c("id", "condition")) %>% 
  mutate(hypothesis_type = factor(hypothesis_type) %>% fct_rev(),
         slider_response_collapsed = factor(slider_response_collapsed) %>% fct_rev()) 
```

## Write to disk. 

```{r}
write_csv(d_final, path = here("/data/02_tidy_data", "goal_actions_tidy_pilotB.csv"))
```

