---
title: "Soc-Info Prior Data Processing"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

```{r}
library(lubridate); library(magrittr); library(jsonlite); 
library(tidyverse); library(here)
```

```{r}
d_path <- "data/01_raw_data/actions_prior/sandbox-results/"
```

## Load raw json data

Write a function that reads the raw json, extacts the information we care about, and builds a tidy data frame. Note that this function is specific to the prior elicitation task, which stores fewer variables.

```{r}
json_to_df_prior <- function(data_path, file) {
  d <- read_json(path = here(data_path, file))
  tibble(
    workerid = d$WorkerId, 
    condition = d$answers$goal_condition,
    action_response = d$answers$action_response,
    browser = d$answers$browser,
    browser_width = d$answers$browser_width,
    browser_height = d$answers$browser_height,
    screen_width = d$answers$screen_width,
    screen_height = d$answers$screen_height,
    mobile_device = d$answers$mobile_device,
    about = d$answers$about,
    comment = d$answers$why_action,
    age = d$answers$age,
    gender = d$answers$gender,
    first_language = d$answers$language
  )
}
```


Use purrr's safely function to catch any errors.

```{r}
safe_json_to_df <- safely(json_to_df_prior)
```

Use purrr to map our read json function over all files in the raw data directory

```{r}
files <- dir(here(d_path))
df_list <- files %>% purrr::map(~ safe_json_to_df(data_path = d_path, .)) 
```

Look at output to see where errors occurred.

```{r}
results <- df_list %>% transpose() 
ok <- results$error %>% map_lgl(is_null)
```

Convert to data frame only keeping succssful function calls.

```{r}
df <- results$result %>% keep(ok) %>%  map_df(bind_rows)
```

## Data checks

How many participants in each condition?

```{r}
df %>% 
  distinct(workerid, condition) %>% 
  count(condition) %>% 
  knitr::kable()
```

Convert all strings to lower case.

```{r}
df %<>% mutate_if(is.character, str_to_lower)
```

## Anonymize Turker ids. 

```{r}
df_anonymized <- df %>% 
  select(workerid) %>% 
  distinct() %>% 
  mutate(id = 1:nrow(.)) 

df_wide <- left_join(df, df_anonymized, by = "workerid") %>% 
  select(id, everything(), -workerid)
```

## Write to disk. 

```{r}
write_csv(df_wide, path = here("/data/02_tidy_data", "goal_actions_prior_tidy.csv"))
```
