---
title: "SOC-INFO Visualization"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE, warning = FALSE, message = FALSE)
```

## Setup

```{r}
library(magrittr); library(tidyverse); library(here) 
theme_set(theme_minimal())
```

Read data. 

```{r}
d_path <- "data/02_tidy_data/"
d <- read_csv(here(d_path, "goal_actions_tidy_pilotB.csv"))
```

```{r}
d %<>% 
  mutate(hypothesis_type = factor(hypothesis_type) %>% fct_rev(),
         slider_response_collapsed = factor(slider_response_collapsed) %>% fct_rev(),
         action_response_collapsed = factor(action_response_collapsed) %>% fct_rev()) 
```


## Table of comments

```{r}
d %>% 
  select(id, age, condition, about) %>% 
  unique() %>% 
  arrange(condition) %>% 
  knitr::kable()
```

## Prior and posterior beliefs

Now summarise and plot.
  
```{r}  
d %>% 
  group_by(hypothesis_type, condition, hypothesis) %>% 
  summarise(m = mean(slider_value_normalized)) %>% 
  ggplot(aes(x = hypothesis, y = m, fill = condition)) +
  geom_bar(stat = "identity", width = 0.4, position = position_dodge()) +
  geom_hline(yintercept = 0.3, linetype = "dashed") +
  lims(y = c(0,1)) +
  scale_fill_grey() +
  ggthemes::theme_few() +
  theme(legend.position = "top") +
  facet_wrap(~hypothesis_type)
```

Same plot but collapsing across the single button hypotheses. 

```{r}
d %>% 
  group_by(hypothesis_type, condition, slider_response_collapsed) %>% 
  summarise(m = mean(slider_value_norm_2)) %>% 
  ggplot(aes(x = slider_response_collapsed, y = m, fill = condition)) +
  geom_bar(stat = "identity", width = 0.4, position = position_dodge()) +
  geom_hline(yintercept = 0.3, linetype = "dashed") +
  lims(y = c(0,1)) +
  scale_fill_grey() +
  ggthemes::theme_few() +
  labs(x = "Hypothesis", y = "Beliefs") +
  theme(legend.position = "top") +
  facet_wrap(~hypothesis_type)
```

## Action responses 

Plot counts of different action responses for the learning vs. performance goal conditions.

```{r}
d %>% 
  select(condition, action_response, id) %>% 
  unique() %>% 
  group_by(action_response, condition) %>% 
  count() %>% 
  group_by(condition) %>% 
  mutate(prop = n / sum(n)) %>% 
  ggplot(aes(x = action_response, y = prop, fill = condition)) +
  geom_bar(stat = "identity", width = 0.4, position = position_dodge()) +
  lims(y = c(0,1)) +
  scale_fill_grey()
```

Plot the distribution using the collapsed action response variable.

```{r}
d %>% 
  select(condition, action_response_collapsed, id) %>% 
  unique() %>% 
  group_by(action_response_collapsed, condition) %>% 
  count() %>% 
  group_by(condition) %>% 
  mutate(prop = n / sum(n)) %>% 
  ggplot(aes(x = action_response_collapsed, y = prop, fill = condition)) +
  geom_bar(stat = "identity", width = 0.4, position = position_dodge()) +
  lims(y = c(0,1)) +
  labs(y = "Prop. Participants", x = "Action Selected") +
  scale_fill_grey()
```

Make a table of the raw counts.

```{r}
d %>% 
  select(condition, action_response_collapsed, id) %>% 
  unique() %>% 
  group_by(action_response_collapsed, condition) %>% 
  count() %>% 
  knitr::kable()
```


## Experiment time distributions

Plot the distribution of overall time on the experiment across conditions.

```{r}
d %>% 
  select(id, experiment_time, condition) %>% 
  unique() %>% 
  ggplot(aes(x = condition, y = experiment_time / 60)) +
  geom_boxplot(width = 0.3) +
  lims(y = c(0,max(d$experiment_time / 60))) +
  labs(y = "Time (min)")
```

Make the same plot, but for the time spent on the action decision.

```{r}
d %>% 
  select(id, action_trial_time, condition) %>% 
  unique() %>% 
  ggplot(aes(x = action_trial_time)) +
  geom_histogram() + 
  facet_wrap(~condition)
  
```

## Plot belief change

```{r}
d %>% 
  ggplot(aes(x = hypothesis_type, y = slider_value_norm_2, color = condition)) +
  geom_line(aes(group = id), size = 1) + 
  geom_jitter(width = 0.03, size = 2) +
  facet_wrap(~slider_response_collapsed) +
  lims(y = c(0,1)) +
  langcog::scale_color_solarized() +
  ggthemes::theme_few() +
  theme(legend.position = "top")
```

Now as a function of which action participants chose

```{r}
d %>% 
  ggplot(aes(x = hypothesis_type, y = slider_value_norm_2, 
             color = condition,
             linetype = action_response_collapsed)) +
  geom_line(aes(group = id), size = 0.5) + 
  geom_jitter(width = 0, size = 2) +
  facet_grid(~slider_response_collapsed) +
  lims(y = c(0,1)) +
  langcog::scale_color_solarized() +
  ggthemes::theme_few() +
  theme(legend.position = "top")
```
