---
title: "SOC-INFO Visualization"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

```{r}
library(magrittr); library(tidyverse); library(here) 
theme_set(theme_minimal())
```

```{r}
d_path <- "data/02_tidy_data/"
d <- read_csv(here(d_path, "goal_actions_tidy.csv"))
```

## Prior and posterior beliefs

Tidy up the data frame.

```{r}
prior <-  d %>% 
  select(id, condition, prior_beliefs, prior_hypothesis) %>% 
  mutate(hypothesis_type = "prior") %>% 
  rename(slider_value = prior_beliefs,
         hypothesis = prior_hypothesis)

posterior <- d %>% 
  select(id, condition, posterior_beliefs, posterior_hypothesis) %>% 
  mutate(hypothesis_type = "posterior") %>% 
  rename(slider_value = posterior_beliefs,
         hypothesis = posterior_hypothesis)
  
d_beliefs <- bind_rows(prior, posterior)
```

Normalize the sliders.

```{r}
d_beliefs %<>% 
  group_by(id, hypothesis_type) %>% 
  mutate(slider_value_normalized = round(slider_value / sum(slider_value), 3)) %>% 
  ungroup()
```

Now summarise and plot.
  
```{r}  
d_beliefs %>% 
  mutate(hypothesis_type = factor(hypothesis_type) %>% fct_rev()) %>% 
  group_by(hypothesis_type, condition, hypothesis) %>% 
  summarise(m = mean(slider_value_normalized)) %>% 
  ggplot(aes(x = hypothesis, y = m, fill = condition)) +
  geom_bar(stat = "identity", width = 0.4, position = position_dodge()) +
  geom_hline(yintercept = 0.3, linetype = "dashed") +
  scale_fill_grey() +
  ggthemes::theme_few() +
  theme(legend.position = "top") +
  facet_wrap(~hypothesis_type)
```

## Action responses 

Plot counts of different action responses for the learning vs. performance goal conditions.

```{r}
d %>% 
  select(condition, action_response) %>% 
  unique() %>% 
  ggplot(aes(x = action_response, fill = condition)) +
  geom_bar(stat = "count", width = 0.4, position = position_dodge()) +
  scale_fill_grey()
```

Now do the same analysis, but collapse across the two single button press options. 

```{r}
d %<>% 
  mutate(action_response_collapsed = ifelse(action_response == "orange_and_purple", 
                                            "both_buttons", 
                                            "single_button"))
```

Plot the distribution using the collapsed action response variable.

```{r}
d %>% 
  select(id, condition, action_response_collapsed) %>% 
  unique() %>% 
  ggplot(aes(x = action_response_collapsed, fill = condition)) +
  geom_bar(stat = "count", width = 0.4, position = position_dodge()) +
  scale_fill_grey()
```

## Experiment time distributions

Plot the distribution of overall time on the experiment across conditions.

```{r}
d %>% 
  select(id, experiment_time, condition) %>% 
  unique() %>% 
  ggplot(aes(x = condition, y = experiment_time)) +
  geom_violin()
```

Make the same plot, but for the time spent on the action decision.

```{r}
d %>% 
  select(id, action_trial_time, condition) %>% 
  unique() %>% 
  ggplot(aes(x = condition, y = action_trial_time)) +
  geom_violin()
```

