---
title: "SOC-INFO Visualization"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

```{r}
library(magrittr); library(tidyverse); library(here) 
theme_set(theme_minimal())
```

```{r}
d_path <- "data/02_tidy_data/"
d <- read_csv(here(d_path, "goal_actions_tidy.csv"))
```

## Prior beliefs

Normalize the sliders.

```{r}
d %<>% 
  group_by(id) %>% 
  mutate(prior_normalized = round(prior_beliefs / sum(prior_beliefs), 3)) 
```

Summarise and plot prior distribution.

```{r}
d %>% 
  group_by(prior_hypothesis) %>% 
  summarise(m_prior = mean(prior_normalized)) %>% 
  ggplot(aes(x = prior_hypothesis, y = m_prior)) +
  geom_bar(stat = "identity", width = 0.4)
```

## Posterior beliefs

Normalize the sliders.

```{r}
d %<>% 
  group_by(id) %>% 
  mutate(posterior_normalized = round(posterior_beliefs / sum(posterior_beliefs), 3))
```

Summarise and plot prior distribution.

```{r}
d %>% 
  group_by(posterior_hypothesis) %>% 
  summarise(m_posterior = mean(posterior_normalized)) %>% 
  ggplot(aes(x = posterior_hypothesis, y = m_posterior)) +
  geom_bar(stat = "identity", width = 0.4)
```

## Action responses 

Plot counts of different action responses for the learning vs. performance goal conditions.

```{r}
d %>% 
  select(id, action_response) %>% 
  unique() %>% 
  ggplot(aes(x = action_response)) +
  geom_bar(stat = "count", width = 0.4)
```

Now do the same analysis, but collapse across the two single button press options. 

```{r}
d %<>% 
  mutate(action_response_collapsed = ifelse(action_response == "orange_and_purple", 
                                            "both_buttons", 
                                            "single_button"))
```

Plot the distribution using the collapsed action response variable.

```{r}
d %>% 
  select(id, action_response_collapsed) %>% 
  unique() %>% 
  ggplot(aes(x = action_response_collapsed)) +
  geom_bar(stat = "count", width = 0.4)
```
