---
title: "SOC-INFO Visualization"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE, warning = FALSE, message = FALSE)
```

## Setup

```{r}
library(magrittr); library(tidyverse); library(here) 
theme_set(theme_minimal())
```

Read data. 

```{r}
d_path <- "data/02_tidy_data/"
d_file_name <- "goal_actions_ver2_tidy_pilot.csv"
d <- read_csv(here(d_path, d_file_name)) 
```

## Table of comments

```{r}
d %>% 
  select(id, age, condition, about, comment) %>% 
  unique() %>% 
  arrange(condition) %>% 
  knitr::kable()
```

```{r}
d %<>% mutate(hypothesis_type = factor(hypothesis_type) %>% fct_rev(),
              hypothesis = factor(hypothesis) %>% fct_rev())
```


## Prior and posterior beliefs

Now summarise and plot.
  
```{r}  
d %>% 
  group_by(hypothesis_type, condition, hypothesis) %>% 
  summarise(m = mean(slider_value_normalized)) %>% 
  ggplot(aes(x = hypothesis, y = m, fill = condition)) +
  geom_bar(stat = "identity", width = 0.4, position = position_dodge()) +
  geom_hline(yintercept = 0.3, linetype = "dashed") +
  lims(y = c(0,1)) +
  scale_fill_grey() +
  ggthemes::theme_few() +
  theme(legend.position = "top",
        axis.text.x = element_text(angle = 45, vjust = 0.5)) +
  facet_wrap(~hypothesis_type)
```

## Action responses 

Plot counts of different action responses for the learning vs. performance goal conditions.

```{r}
d %>% 
  select(condition, action_response, id) %>% 
  unique() %>% 
  count(action_response, condition) %>% 
  group_by(condition) %>% 
  mutate(prop = n / sum(n)) %>% 
  ggplot(aes(x = action_response, y = prop, fill = condition)) +
  geom_bar(stat = "identity", width = 0.4, position = position_dodge()) +
  lims(y = c(0,1)) +
  scale_fill_grey() +
  facet_grid(.~condition)
  
```

Make a table of the raw counts.

```{r}
d %>% 
  select(condition, action_response, id) %>% 
  unique() %>% 
  count(action_response, condition) %>% 
  knitr::kable()
```

## Experiment time distributions

Plot the distribution of overall time on the experiment across conditions.

```{r}
d %>% 
  select(id, experiment_time, condition) %>% 
  unique() %>% 
  ggplot(aes(x = condition, y = experiment_time / 60)) +
  geom_boxplot(width = 0.3) +
  lims(y = c(0,max(d$experiment_time / 60))) +
  labs(y = "Time (min)")
```

Make the same plot, but for the time spent on the action decision.

```{r}
d %>% 
  select(id, action_trial_time, condition) %>% 
  unique() %>% 
  ggplot(aes(x = action_trial_time)) +
  geom_histogram() + 
  labs(x = c("time (sec)")) +
  facet_wrap(~condition)
```

## Plot belief change

```{r}
d %>% 
  ggplot(aes(x = hypothesis_type, y = slider_value_normalized, color = condition)) +
  geom_line(aes(group = id), size = 1) + 
  geom_jitter(width = 0.03, size = 2) +
  facet_wrap(~hypothesis) +
  lims(y = c(0,1)) +
  langcog::scale_color_solarized() +
  ggthemes::theme_few() +
  theme(legend.position = "top")
```

Now make the same plot, but as a function of which action participants chose

```{r}
d %>% 
  ggplot(aes(x = hypothesis_type, y = slider_value_normalized, 
             color = condition,
             linetype = action_response)) +
  geom_line(aes(group = id), size = 0.5) + 
  geom_jitter(width = 0, size = 2) +
  facet_grid(~hypothesis) +
  lims(y = c(0,1)) +
  langcog::scale_color_solarized() +
  ggthemes::theme_few() +
  theme(legend.position = "top")
```
